Classifier Testing

### 2019-04-17 Code/dallin_annotations/02_visualize_twitter_data.Rmd
General reoganization of the dallin_annotations folder. This folder is meant to replace the rest of the code in the repository. It's the same code as before, just renamed and with more documentation.

This file is meant to take our twitter data and produce a few visualizations on the data.

>>>>

This file is meant to take our twitter data and produce a few visualizations. These visualizations helped us explore the tweets and get a generic grip on what people tweeted about in relation to these airlines. Understanding the data better helped us move forward with our analysis and model building.

### 2019-04-17 Code/dallin_annotations/03_analyze_complaint_categories.Rmd
General reoganization of the dallin_annotations folder. This folder is meant to replace the rest of the code in the repository. It's the same code as before, just renamed and with more documentation.

# Read in the Labeled Tweets
```{r}
# Note that the labeled tweet data is kept in my Temporary folder
data <- read_csv("../Temporary/Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv")
```

>>>>

# Read in the Labeled Tweets
```{r}
# Note that the labeled tweet data is kept in my Temporary folder in the train_test_data folder
data <- read_csv("../../Temporary/train_test_data/Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv")
```

### 2019-04-17 Code/dallin_annotations/09_classifier_testing.Rmd
General reoganization of the dallin_annotations folder. This folder is meant to replace the rest of the code in the repository. It's the same code as before, just renamed and with more documentation.

### What scripts need to function for this code to work?
##### predict_func.R
* Renamed as 11_predict_func.Rmd in this folder.
* NOT WORKING

##### TweetComplaintPredictor.r
* Renamed as 12_tweet_complaint_predictor.Rmd in this folder.
* NOT WORKING

@@

##### model50-tweet_sample_2M_noRT.dat.bin 
* It looks like this is a fasttext model, but I'm not sure if it is the supervised or unsupervised.
* NOT FOUND

@@

# Libraries
```{r}
library(fastrtext)
library(Matrix)
library(xgboost)
source("11_predict_func.Rmd") # Formerly "R/predict_func.R" in Adriel's original code
source("tweet_complaint_predictor.Rmd") # Formerly "R/TweetComplaintPredictor.r" in Adriel's original code
```

@@

# Load Models
```{r}
load("../../Temporary/prcomp4.dat") # Formerly "complaint-prediction/models/fullClassifierOne/prcomp4.dat" in Adriel's original code
fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
load("../../Temporary/xgb.modelPC4.dat") # Formerly "complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat" in Adriel's original code
TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, PC4)

>>>>

### What scripts need to function for this code to work?
##### predict_func.R
* Renamed as 11_predict_func.Rmd in this folder.
* FOUND
* WORKING

##### TweetComplaintPredictor.r
* Renamed as 12_tweet_complaint_predictor.Rmd in this folder.
* FOUND
* NOT WORKING

@@

##### model50-tweet_sample_2M_noRT.dat.bin 
* It looks like this is a fasttext model, but I'm not sure if it is the supervised or unsupervised.
* FOUND
* NOT WORKING
* It must have been large enough that it couldn't be shared on github
* Found in the classifier_construction file (which is dependent on "R/clus_func.R" and "R/logit_classifier_func.R"

@@

# Libraries
```{r}
library(fastrtext)
library(Matrix)
library(xgboost)
source("../complaint-prediction/R/predict_func.Rmd") # Formerly "R/predict_func.R" in Adriel's original code
source("tweet_complaint_predictor.Rmd") # Formerly "R/TweetComplaintPredictor.r" in Adriel's original code
```

@@

# Load Models
```{r}
load("../../Temporary/prcomp4.dat") # Formerly "complaint-prediction/models/fullClassifierOne/prcomp4.dat" in Adriel's original code
fasttextModel <- load_model("complaint-prediction/models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat.bin")
# Model50 was built in fasttext_clust_EDA

load("../../Temporary/xgb.modelPC4.dat") # Formerly "complaint-prediction/models/fullClassifierOne/xgb.modelPC4.dat" in Adriel's original code
TweetComplaintPredictor <- newTweetComplaintPredictor(fasttextModel, train.pr, bst, PC4)
